Paper Visualizations

### 2022-05-09 eda/paper-graphics.Rmd
paper graphics

amici_ct_plt
```
Check spike
```{r}
df %>% filter(lubridate::year(ddate2) == 1989) %>% distinct(case, ddate2, cfemam, coppam)
```

>>>>

ggsave("graphics/avg_amici_time.png",amici_ct_plt, height = 5, width = 8)
amici_ct_plt
```
Check spike
```{r}
df %>% filter(lubridate::year(ddate2) == 1989) %>% distinct(case, ddate2, cfemam, coppam)
```
